### 2018-09-10 ICRA19/relatedWork.tex
edited related work a little bit.

Controlling the \emph{shape}, or relative positions, of a swarm of robots is a key ability for a range of applications.  Correspondingly, it has been studied from a control-theoretic perspective in  both centralized and decentralized approaches. For examples of each, see the centralized virtual leaders in \cite{egerstedt2001formation}, and the  gradient-based decentralized controllers  using control-Lyapunov functions in~\cite{hsieh2008decentralized}. However, these approaches assume a level of intelligence and autonomy in individual robots that exceeds the capabilities of many systems, including current micro- and nano-robots.  Current micro- and nano-robots, such as those in~\cite{Chowdhury2015,martel2015magnetotactic,Xiaohui2015magnetiteMicroswimmers} lack onboard computation.

This paper focuses on centralized techniques that apply the same control input to both particles. 
Precision control requires breaking the symmetry caused by the uniform input.  
Symmetry can be broken using particles that respond differently to the uniform control signal, either through agent-agent reactions \cite{bertozzi2015ring}, or engineered inhomogeneity  \cite{Donald2013,bretl2007,beckerIJRR2014}. 
 The magnetic gradients of MRI scanners are \emph{uniform}, meaning the same force is applied everywhere in the workspace\cite{nosrati2018development}.
 This work assumes a uniform control with homogenous particles, as in~\cite{AaronManipulation2013}, and breaks the control symmetry using obstacles in the workspace.

@@

%\emph{Artificial Force-fields:}
%Much research has focused on generating non-uniform artificial force-fields that can be used to rearrange passive components. 
Alternative techniques rely on non-uniform inputs, such as artificial force-fields.
Applications have included techniques to design shear forces for sensorless manipulation of a single object by~\cite{lamiraux+2001:ra}.  
\cite{vose2012sliding} demonstrated a collection of 2D force fields generated by six degree-of-freedom vibration inputs to a rigid plate.  These force fields, including shear forces, could be used as a set of primitives for motion control to steer the formation of multiple objects. %However unlike the uniform control model in this paper, their control was multi-modal and position-dependent.
%\todo{talk about obstacles, think about adding goldberg}

%This paper develops control algorithms using uniform control fields, such as the magnetic resonance navigation \cite{nosrati2018development}.%field in a clinical MRI [insert a recent reference from Sylvain Martel using MRI].
Similarly, much recent work in magnet control has focused on exploiting inhomogeneities in the magnetic field to control multiple micro particles  using gradient-based pulling~\cite{Salmanipour2018EightDOF,Denasi2018independent}.  
Unfortunately, using large-scale external magnetic fields makes it challenging to independently control more than one microrobot unless the  distance between the electromagnetic coils is at the same length scales as the robot workspace~\cite{diller2016six, Denasi2018independent, Salmanipour2018EightDOF }. In contrast, % to methods that exploit inhomogeneities in the magnetic field to control multiple micro particles, e.g. \cite{Denasi2018independent}, that exploited nonlinearities generated by four magnetic coils in close proximity to the workspace to achieve trajectory control of two microspheres, 
 this paper requires only a controllable constant gradient in orthogonal directions to position the particles.
% Systems like this one are poorly suited for PRM and RRT*-type methods\cite{lavalle2006planning} because if during a movement a collision occurs, that movement is irreversible.
   %Flow in a pipe or body lume

>>>>

Shape, or relative position, control of many particles is necessary for a range of applications. Therefore, it has been a topic of research from a control perspective in both centralized and distributed approaches. 
 This paper focuses on centralized approach that apply the uniform control input to all the particles. To change the relative position of the particles, we need to break the symmetry caused by the uniform input.
Symmetry can be broken using particles that respond differently to the uniform control signal, either through agent-agent reactions \cite{bertozzi2015ring}, or engineered inhomogeneity  \cite{Donald2013,bretl2007,beckerIJRR2014}. 
 The magnetic gradients of MRI scanners are \emph{uniform}, meaning the same force is applied everywhere in the workspace\cite{nosrati2018development}.
%Controlling the \emph{shape}, or relative positions, of many particles is a key ability for a range of applications.  Correspondingly, it has been studied from a control-theoretic perspective in  both centralized and decentralized approaches.
% For examples of each, see the centralized virtual leaders in \cite{egerstedt2001formation}, and the  gradient-based decentralized controllers  using control-Lyapunov functions in~\cite{hsieh2008decentralized}. 
%However, these approaches assume a level of intelligence and autonomy in individual robots that exceeds the capabilities of many systems, including current micro- and nano-robots.  Current micro- and nano-robots, such as those in~\cite{Chowdhury2015,martel2015magnetotactic,Xiaohui2015magnetiteMicroswimmers} lack onboard computation.

%This paper focuses on centralized techniques that apply the same control input to both particles. 
%Precision control requires breaking the symmetry caused by the uniform input.  
%Symmetry can be broken using particles that respond differently to the uniform control signal, either through agent-agent reactions \cite{bertozzi2015ring}, or engineered inhomogeneity  \cite{Donald2013,bretl2007,beckerIJRR2014}. 
% The magnetic gradients of MRI scanners are \emph{uniform}, meaning the same force is applied everywhere in the workspace\cite{nosrati2018development}.
 This work assumes a uniform control with homogenous particles, as in~\cite{AaronManipulation2013}, and breaks the control symmetry using obstacles in the workspace.

@@

%\emph{Artificial Force-fields:}
%Much research has focused on generating non-uniform artificial force-fields that can be used to rearrange passive components.

Alternative techniques rely on non-uniform inputs, such as artificial force-fields. 
Much recent work in magnet control has focused on exploiting inhomogeneities in the magnetic field to control multiple micro particles using gradient-based pulling~\cite{Salmanipour2018EightDOF,Denasi2018independent}.  
Using large-scale external magnetic fields makes it challenging to independently control more than one microrobot unless the distance between the electromagnetic coils is at the same length scales as the robot workspace~\cite{diller2016six, Denasi2018independent, Salmanipour2018EightDOF }.
%Applications have included techniques to design shear forces for sensorless manipulation of a single object by~\cite{lamiraux+2001:ra}.  
%\cite{vose2012sliding} demonstrated a collection of 2D force fields generated by six degree-of-freedom vibration inputs to a rigid plate.  These force fields, including shear forces, could be used as a set of primitives for motion control to steer the formation of multiple objects. %However unlike the uniform control model in this paper, their control was multi-modal and position-dependent.
%\todo{talk about obstacles, think about adding goldberg}

%This paper develops control algorithms using uniform control fields, such as the magnetic resonance navigation \cite{nosrati2018development}.%field in a clinical MRI [insert a recent reference from Sylvain Martel using MRI].
 %In contrast, % to methods that exploit inhomogeneities in the magnetic field to control multiple micro particles, e.g. \cite{Denasi2018independent}, that exploited nonlinearities generated by four magnetic coils in close proximity to the workspace to achieve trajectory control of two microspheres, 
% this paper requires only a controllable constant gradient in orthogonal directions to position the particles.
% Systems like this one are poorly suited for PRM and RRT*-type methods\cite{lavalle2006planning} because if during a movement a collision occurs, that movement is irreversible.
   %Flow in a pipe or body lume
